Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-11-27 leadership_across_cultures_contexts.Rmd
Commenting out jaccard plotting for now. Also not evaluating tables because csv files not available.

Table: (\#tab:qualfuncvars) Operational definitions for coded leader qualities and functions.

```{r qualfuncvars, echo=FALSE, message=F, warning=FALSE}
library(readr)
qual_func_var_tab<-read_csv('func_qual_definitions.csv', na = 'NA')
library(knitr)
kable(qual_func_var_tab)
```

@@

Table: (\#tab:costbenefitvars) Operational definitions for coded benefits and costs for leaders and followers.

```{r costbenefitvars, echo=FALSE, message=F, warning=FALSE, }
library(readr)
cost_benefit_vars_tab<-read_csv('costs_benefits.csv', na = 'NA')
library(knitr)
kable(cost_benefit_vars_tab)
```

@@

A logistic PCA on the `r length(quality_vars)` coded leader quality variables, with rank $k=`r dim(logpca_model_qualities$U)[2]`$ optimized by cross-validation, explained `r signif(logpca_model_qualities$prop_deviance_expl, 3)*100`% of the deviance. We draw on the first of the three leader quality components for interpretation and additional analyses and identify this component as a *Prestige vs. Dominance* measure. Low values on Leader qualities PC 1 (Prestige vs. Dominance) are strongly associated with the variables *Experienced/accomplished* and *Knowledgeable/intelligence* and moderately associated with *Oratory skill* and *Innovative*. High values are strongly associated with *Polygnous* and *Coercive authority* and moderately associated with *Many children* and *High quality spouse*. Therefore, the "dominance" side of the *Prestige vs. Dominance* component is also closely liked to reproduction. Measures of physical formidability and aggressiveness are also moderately associated with the "dominance" side of this component. See Figure \@ref(fig:qualitiesPCplot).

@@

Similarly, A logistic PCA on the `r length(quality_vars)` coded leader quality variables, with rank $k=`r dim(logpca_model_functions$U)[2]`$ optimized by cross-validation, `r signif(logpca_model_functions$prop_deviance_expl, 3)*100`% of the deviance. The first Leader functions component distinguishes between interpersonal mediation functions and group organizational and social functions, we define as a *Mediation vs. Organization* measures. Low values on Leader functions PC 1 (Mediation vs. Organization) are strongly associated with the variables *Resolve conflict* and *Provide counsel/direction* and moderately associated with *Political appointments* and *Punishment*, whereas high values are strongly associated with *Social functions* and *Organize cooperation* and moderately associated with *Ritual functions*. See Figure \@ref(fig:functionsPCplot).

>>>>

```{r qualfuncvars, echo=FALSE, message=F, warning=FALSE, eval=F}
library(readr)
qual_func_var_tab<-read_csv('func_qual_definitions.csv', na = 'NA')
library(knitr)
kable(qual_func_var_tab, caption = "Operational definitions for coded leader qualities and functions.")
```

@@

```{r costbenefitvars, echo=FALSE, message=F, warning=FALSE, eval=F}
library(readr)
cost_benefit_vars_tab<-read_csv('costs_benefits.csv', na = 'NA')
library(knitr)
kable(cost_benefit_vars_tab, caption = "Operational definitions for coded benefits and costs for leaders and followers.")
```

@@

A logistic PCA on the `r length(quality_vars)` coded leader quality variables, with rank $k=`r dim(logpca_model_qualities$U)[2]`$ optimized by cross-validation, explained `r signif(logpca_model_qualities$prop_deviance_expl, 3)*100`% of the deviance. We draw on the first two leader quality components for interpretation and additional analyses and identify this component as a *Prestige vs. Dominance* measure. Low values on Leader qualities PC 1 (Prestige vs. Dominance) are strongly associated with the variables *Experienced/accomplished* and *Knowledgeable/intelligence* and moderately associated with *Oratory skill* and *Innovative*. High values are strongly associated with *Polygnous* and *Coercive authority* and moderately associated with *Many children* and *High quality spouse*. Therefore, the "dominance" side of the *Prestige vs. Dominance* component is also closely liked to reproduction. Measures of physical formidability and aggressiveness are also moderately associated with the "dominance" side of this component. See Figure \@ref(fig:qualitiesPCplot).

@@

Similarly, A logistic PCA on the `r length(function_vars)` coded leader function variables, with rank $k=`r dim(logpca_model_functions$U)[2]`$ optimized by cross-validation, `r signif(logpca_model_functions$prop_deviance_expl, 3)*100`% of the deviance. The first Leader functions component distinguishes between interpersonal mediation functions and group organizational and social functions, we define as a *Mediation vs. Organization* measures. Low values on Leader functions PC 1 (Mediation vs. Organization) are strongly associated with the variables *Resolve conflict* and *Provide counsel/direction* and moderately associated with *Political appointments* and *Punishment*, whereas high values are strongly associated with *Social functions* and *Organize cooperation* and moderately associated with *Ritual functions*. See Figure \@ref(fig:functionsPCplot).
